Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
5 Experimental Evaluation

This section is split into three parts. The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation. Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as \textcolor{blue}{presented by}~\cite{Mann2007}.

>>>>

This section is split into three parts. The setup is described in Section~\ref{Experimental-Setup}, while Section~\ref{Benchmarks-Description} describes all benchmarks that were used for performing the experimental evaluation. Section~\ref{Experimental-Results} reports a comparison among MATLAB, ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z using a set of standard HW-SW partitioning benchmarks, as \textcolor{blue}{presented by}~\cite{Mann2007}.
